A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-26 doc/paper1-submission/paper5-adjusted.tex
Unify Figure 1.
Unify Figure 2.
Unify Fig4
Unify Fig5
Unify Figure 6.
Convert Fig7
Convert Fig9
Unify Fig12

\begin{figure}
\subfloat[Input tree 1]{\includegraphics[width=0.45\textwidth]{Fig1a}

}\hfill{}\subfloat[Input tree 2]{\includegraphics[width=0.45\textwidth]{Fig1b}

\subfloat[Summary tree]{\includegraphics[width=0.45\textwidth]{Fig1c}

}\hfill{}\subfloat[Summary tree]{\includegraphics[width=0.45\textwidth]{Fig1d}

@@

\begin{figure}
\subfloat[Input tree 1]{\includegraphics[scale=0.57]{Fig2a}

}\hfill{}\subfloat[Input tree 2]{\includegraphics[scale=0.57]{Fig2b}

}\hfill{}\subfloat[Input tree 3]{\includegraphics[scale=0.57]{Fig2c}

\subfloat[Summary tree]{\includegraphics[scale=0.57]{Fig2d}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.57]{Fig2e}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.57]{Fig2f}

@@

\begin{figure}
\subfloat[Tree 1]{\includegraphics[scale=0.4]{Fig4a}

}\hfill{}\subfloat[Tree 2]{\includegraphics[scale=0.4]{Fig4b}

}\hfill{}\subfloat[Taxonomy Tree]{\includegraphics[scale=0.4]{Fig4c}

@@

\begin{figure}
\subfloat[Tree 1]{\includegraphics[scale=0.4]{Fig5a}

}\hfill{}\subfloat[Tree 2]{\includegraphics[scale=0.4]{Fig5b}

}\hfill{}\subfloat[Pruned taxonomy tree $\protect\prunedTaxonomy$]{\includegraphics[scale=0.4]{Fig5c}

@@

\begin{figure}
  \subfloat[Subproblem \emph{ABCD}]{\includegraphics[width=0.3\textwidth]{Fig6a}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Fig6b}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Fig6c}

  \subfloat[Subproblem \emph{root}]{\includegraphics[width=0.3\textwidth]{Fig6d}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Fig6e}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Fig6f}

\caption{Subproblems \emph{ABCD} and \emph{root} generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.57]{Fig7a}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7b}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7c}

\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7d}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7e}

}\hfill{}

@@

\begin{figure}
\hfill{}\subfloat[Solution to subproblem \emph{ABCD}]{\includegraphics[scale=0.55]{Fig9a}

}\hfill{}\subfloat[Solution to subproblem \emph{root}]{\includegraphics[scale=0.55]{Fig9b}

}\hfill{}

@@

\begin{figure}
\begin{centering}
\subfloat[Taxonomy]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{Fig12a}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}\subfloat[Grafted solution]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{Fig12b}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}
\par\end{centering}
\begin{centering}
\subfloat[Unpruned tree - broken taxa removed]{\begin{centering}
\includegraphics[scale=0.38]{Fig12c}
\par\end{centering}
}\hfill{}\subfloat[Unpruned tree with MRCA-attachment]{\begin{centering}
\includegraphics[scale=0.38]{Fig12d}
\par\end{centering}
}
\par\end{centering}
\caption{\label{fig:Two-approaches-to-unpruning}Two approaches to unpruning.
Taxa G and R in the taxonomy (a) are broken because they conflict
with the grafted solution (b). Removing these broken taxa from the
taxonomy before unpruning leads to taxa R4, R5, and R6 being attached
directly at taxon N, as in tree (c). In tree (d), the children of
the broken taxon R are instead attached at the MRCA of R1, R2, and
R3. Our method follows the second approach.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig1}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig2}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig4}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig5}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig6}

\caption{Subproblems \emph{ABCD} and \emph{root} generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig7}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig9}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig12}

\caption{\label{fig:Two-approaches-to-unpruning}Two approaches to unpruning.
Taxa G and R in the taxonomy (a) are broken because they conflict
with the grafted solution (b). Removing these broken taxa from the
taxonomy before unpruning leads to taxa R4, R5, and R6 being attached
directly at taxon N, as in tree (c). In tree (d), the children of
the broken taxon R are instead attached at the MRCA of R1, R2, and
R3. Our method follows the second approach.}
\end{figure}
